%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX Template
% Version 1.0 (14/7/16)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Coursework Section
\newcommand\skills{ 

    \text{Data Structures}  \newline
    \text{Object Oriented Programming}  \newline
    \text{Operating Systems} \newline
    \text{Computer Architecture} \newline
    \text{Programming: Penetration Testing} \newline
    \text{Programming Languages}  \newline
    \textsc{Computer Security} \newline
    \text{Encryption}  \newline
    \text{Discrete Mathematics}  \newline
    \text{Applied Linear Algebra}  \newline
    
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

\cvname{John Rader} 
\cvjobtitle{Software Engineer} 
\cvlinkedin{/in/john-rader}
\cvgithub{JohnRader}
\cvnumberphone{(815) 641-2846} 
\cvmail{jcrader238@gmail.com} 

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar
%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
    \textbf{Lewis University }\text{| BS in Computer Science | GPA (3.4/4)}\newline
    \textnormal{May 2018 | Romeoville, IL}
%----------------------------------------------------------------------------------------
%	 AWARDS AND POSITIONS
%----------------------------------------------------------------------------------------
\section{Awards and Positions}
    \text{Dean's List} \newline
    \text{Best Buy Award of Excellence} \newline
    \text{Cyber-Security Group Member} \newline
    \text{LU LaSallian Grant} \newline
    \text{Tutor/Judge, Robotic Engineering Challenge for High School Students, Joliet Junior College}
%-----------------------------------------------------------------------------------------
%   PROJECTS
%-----------------------------------------------------------------------------------------
\section{Projects}

\textbf{Computer Infrastructure Capstone Project }\text{| Computer Networking}\newline
\text{I worked with three other students in the design, implementation and testing of a medium-to-large networked computer system for a not-for-profit community organization. Additionally, we covered topics in professional ethics, intellectual properties, privacy and professional communication.}\newline

\textbf{Swiss Army Knife Application }\text{| Java}\newline
\text{A Java developed program focusing on the use of Object-Oriented Programming to pull data from a given URL using a single thread or multi-threading. }\newline

\textbf{Python Buffer Overflow }\text{| Python on Kali VM with FreeFloat STP Server} \newline
\text{A Python script designed to establish an FTP connection to a server running on a Windows VM to identify the vulnerability to the buffer overflow exploit. Using the exploit, the script is able to inject a shellcode to allow for remote access on the targeted FreeFloat STP Server.}\newline

\textbf{File Encryptor }\text{| Java}\newline
\text{Java developed app used to encrypt any given text file using four different encryption methods. }\newline

\textbf{SSH Brute Force }\text{| Python} \newline
\text{A Python script designed to brute force into a given host using passwords from a given list or by generating its own passwords. Once there are three incorrect attempts, the connection is dropped and it attempts to reinitialize the SSH connection.}

%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{Oct 2014 -}
		{Present}
        {Inventory Specialist/Sales Associate}
        {\href{http://bestbuy.com}{Best Buy}}
        {}
        {\begin{itemize}
        \item Oversaw back of store logistical operations.
        \item Trained two to three new employees quarterly and ran a team of up to five.
        \item Prepared and filed credit card application into our database and contacted the bank when necessary. 
        \item Accurately and efficiently logged all daily shipping and receiving orders in database.
        \item Worked with clients in person and over the phone to evaluate personal computing needs.
        
        \end{itemize}}
        \\
	\twentyitem
    	{June 2013 -}
		{Oct 2014}
        {Service Clerk}
        {\href{http://www.jewelosco.com}{Jewel-Osco}}
        {}
        {\begin{itemize}
        \item Assisted customers with resolving store and product complaints.
        \item Processed roughly 50 cash/credit transactions per shift.
        
    \end{itemize}}
    \\   
    
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

\end{document} 
